Think deep for reef resilience

### 2025-08-12 paper/paper_draft.qmd
Small tweak to conclusion
To be revisited once all complete

In conclusion, our results suggest that when modelled as part of a large and complex
ecosystem, reef depth is a key factor contributing to ongoing reef resilience. We provide
evidence in support of depth as a form of thermal refugia for shallow-water reefs on the
GBR. While protecting ‘key node’ reefs in larval connectivity networks is an important
consideration for reef restoration efforts [@anthony2020; @hock2017], our results suggest
that current connectivity modelling methods are not able to generate connectivity that
contributes to reef resilience under projected conditions. We suggest further analyses that
investigate the benefits of incorporating depth-based resilience into reef decision making,
as well as further research and development in connectivity modelling methods for
whole-ecosystem scales.

>>>>

The results presented herein suggest that when modelled as part of a large and complex
ecosystem, reef depth is a key factor contributing to ongoing reef resilience. We provide
evidence in support of depth as a form of thermal refugia for shallow-water reefs on the
GBR. While protecting ‘key node’ reefs in larval connectivity networks is an important
consideration for reef restoration efforts [@anthony2020; @hock2017], our results suggest
that current connectivity modelling methods are not able to generate connectivity that
contributes to reef resilience under projected conditions **\[TI: TO BE REVISITED\]**. We
suggest further analyses that investigate the benefits of incorporating depth-based
resilience into reef decision making, as well as further research and development in
connectivity modelling methods for whole-ecosystem scales.
